---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  cache = TRUE
)
```

**This is highly experimental**

![](https://img.shields.io/badge/lifecycle-experimental-orange.svg)



# namespaces

The goal of namespaces is to find minimal versions of dependencies of a package 
by inspecting `NAMESPACE` and `DESCRIPTION` files of those dependencies from the 
[r-pkg.org CRAN mirror](https://github.com/cran). The method hence does not 
ensure the minimal version found is enough to make the code work, it just 
ensures that functions imported from dependencies were exported in those 
package versions indicated in `DESCRIPTION`. 


## Example

You can find out in which release an object was exported for the first time.
```{r}
library("namespaces")
find_first_release("dplyr", "mutate")
```

You can collect all minimal dependencies of a package by inspecting 
masked function calls (`pkg::fun()`) in your source code and the `NAMESPACE` of
the package
```{r}
library("dplyr")
collect_minimal_dependencies() %>%
  group_by(package) %>%
  summarize(min(first_release))
```

If you want to do namespaces analysis, you can also parse any namespace from
any package from CRAN.

```{r}
parse_cran_namespace("xgboost")
```

Or a local name space:
```{r}
parse_local_namespace(here::here())
```


You can update all `DESCRIPTION` entries to match the minimal versions 
required found with the above function.
```{r, eval = FALSE}
# write_minimal_dependencies() # does not yet work.
```

